\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-13 doc/sw-system.tex
First attempt at conclusions, closes #45

\todo{Phil}{write conclusions (\#45).}

Summary of system.

@@

Crowd-sourced gravitational lens detection works, in terms of the
classification of the training set as described here, in the following
specific ways:

@@

\item Participation (crowd size, activity rate) enabled project completion

\item Both \StageOne and \StageTwo achieved the required rejection rates

\item Integrated humanpower = X (\StageOne) and Y (\StageTwo), cf hours taken by
small team of experts

\item Nightly processing is inefficient: more classifications were made than
was necessary during peak participation. Need kafka...

\item Retirement rate. False negatives: which sims were missed?

\item The optimal true positive rate (completeness) and false positive rate in
the training set were estimated to be TPR\% and FPR\% at \StageOne, assuming a
detection threshold of xxx.

\item In the ``refinement'' \StageTwo, X\% of the \StageOne candidates were
rejected (with P less than threshold), and the remainder assigned lens
``probabilities.'' Ranking
subjects by their \StageTwo lens probability gives an ROC curve for the system
with X properties. The optimal true positive rate (completeness) and false
positive rate in the training set were estimated as TPR\% and FPR\%;

\item The lens-finding crowd shows some interesting properties, with
consequences for future scalability

\item The information comes predominantly from volunteers with agents with P =
...

\item The agents show a high mean information per classification, which
increased/decreased with time; this does/doesn?t correlate with active crowd
size, showing how the crowd changed over time...

@@

Sum up, end. \SW provides a lens candidate detection service, crowd-sourcing the
time-consuming work of visually inspecting astronomical images for
gravitationally-lensed features. We invite survey teams searching for lenses in
their wide-field imaging data to contact us if they would like our help.

>>>>

We have designed, implemented and tested a system for   detecting new strong
gravitational lens candidates in wide field imaging surveys by crowd-sourced
visual inspection. The \SW web-based classification interface presents carefully
prepared color composite sky images to volunteers, who mark features they
propose to  have been lensed. The participants receive ongoing training with a
mixture of simulated lens and known-to-be-empty images, and we use this
information to inform the automated interpretation of their markers. In our
first lens search we simply divided the CFHTLS imaging into some 430,000 tiles,
and collected over 10~million volunteer image classifications.

@@

By analyzing the  classifications made of the training set, we conclude that
gravitational lens detection by crowd-sourced visual inspection works,  and in
the following specific ways:

@@

\item Participation levels were high (over 36,000 volunteers, contributing
classifications at rates between $10^3$ and $10^4$ images per hour), suggesting
that if this can be maintained, visual inspection of tens of thousands of images
can be performed on timescales of a few weeks.

\item Over the course of the two stages of the CFHTLS project, the
set of images was reduced by a factor of $10^3$ (from a few hundred thousand to
a few hundred), enough for an expert team to take over.

\item The ``skill'' of the volunteers correlates strongly with the number of
images they have classified.  Quantifying the ``contribution'' as the integrated
skill over the test subjects  classified, we find that about 90\% of the
contribution was made by a few  hundred volunteers -- but that the width of the
skill distribution means that a  few thousand volunteers could have made
comparable contributions, had they classified more images.

\item The optimal true positive rate (completeness) and false positive rate in
the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
2). This  FPR translates to a purity of 20\%.

\item The simulated gravitational lenses that were missed were predominantly
galaxy-scale lenses with faint blue galaxy sources, whose lensed features are
difficult to distinguish from the light from the lens galaxy. We observed some
additional scatter, with some simulated lenses accumulating low probability
simply due to classification noise.

@@

In \PaperTwo we present the results of this CFHTLS lens search in more detail,
in particular focusing on the detection of real lenses, and the comparison
between \SW and various automated lens finding methods. In this paper  we have
shown how \SW provides a lens candidate detection service, crowd-sourcing the
time-consuming work of visually inspecting astronomical images for
gravitationally-lensed features. We invite survey teams searching for lenses in
their wide-field imaging data to contact us if they would like our help.
